Seagrass mapping and monitoring \\ along the coasts of Crete, Greece

### 2011-02-05 MScDiplom_Lemenkova.tex
Comment 13 of Valentijn: combined plots of MODIS, MERIS, CZCS and SeaWiFS sensors

The results enable to study reflectance properties of the seagrass and other
seafloor types. Application of the optical radiative transfer model WASI is suggested to simulate
remote sensing sensors (\ac{MODIS}, \ac{ASTER}, \ac{MERIS} and \ac{SeaWiFS}), (Fig.\ref{fig:4.6}).

\begin{figure}[h]
	\centering
	\subfloat [CZCS]{\label{fig:29a}\includegraphics[width=0.4\textwidth]{Fig-35a.jpg}}
	\subfloat [MERIS]{\label{fig:29b}\includegraphics[width=0.4\textwidth]{Fig-35b.jpg}}\\
	\subfloat [MODIS]{\label{fig:29c}\includegraphics[width=0.4\textwidth]{Fig-35c.jpg}}
	\subfloat [SeaWiFS]{\label{fig:29d}\includegraphics[width=0.4\textwidth]{Fig-35d.jpg}}
	\caption{Simulated remote sensing reflectance of \textit{P.oceanica} at various sensors}
	\label{fig:4.6}
\end{figure}

@@

\begin{figure}[h]
	\begin{center}
		\includegraphics[scale=0.22]{GNU-10.jpg}
		\caption{Spectral reflectance of the seawater without sediments. Interpolation graph. \href{http://www.gnuplot.info/}{Gnuplot} display­}
		\label{fig:A.24}
	\end{center}
\end{figure}

>>>>

The results enable to study reflectance properties of the seagrass and other
seafloor types. Application of the optical radiative transfer model WASI is suggested to simulate
remote sensing sensors (\ac{MODIS}, \ac{ASTER}, \ac{MERIS} and \ac{SeaWiFS}), (Fig.\ref{fig:4.6}, Fig.\ref{fig:4.6W}).

\begin{wrapfigure}{r}{0.5\textwidth}
	\centering
	\includegraphics[scale=0.45]{Sensors.png}
	\caption{Combined plots of simulated remote sensing reflectance of \textit{P.oceanica} at various sensors: MODIS, MERIS, SeaWiFS and CZCS.}
	\label{fig:4.6}
\end{wrapfigure}

@@

\begin{figure}[H]
	\begin{center}
		\includegraphics[scale=0.22]{GNU-10.jpg}
		\caption{Spectral reflectance of the seawater without sediments. Interpolation graph. \href{http://www.gnuplot.info/}{Gnuplot} display­}
		\label{fig:A.24}
	\end{center}
\end{figure}

\begin{figure}[H]
	\centering
	\subfloat [CZCS]{\label{fig:29a}\includegraphics[width=0.4\textwidth]{Fig-35a.jpg}}
	\subfloat [MERIS]{\label{fig:29b}\includegraphics[width=0.4\textwidth]{Fig-35b.jpg}}\\
	\subfloat [MODIS]{\label{fig:29c}\includegraphics[width=0.4\textwidth]{Fig-35c.jpg}}
	\subfloat [SeaWiFS]{\label{fig:29d}\includegraphics[width=0.4\textwidth]{Fig-35d.jpg}}
	\caption{WASI-simulated remote sensing reflectance of \textit{P.oceanica} at various sensors}
	\label{fig:4.6W}
\end{figure}
